Ribosome accumulation during early phase resistance training

### 2020-09-15 manuscript.Rmd
update method

---
title: "Ribosome accumulation during early phase resistance training"
author: Daniel Hammarström^1,2,£^&ast;,Sjur Øfsteng^2,£^, Bent R. Rønnestad^2^, Stian Ellefsen^1,3^
date: ""
header-includes:
  - \usepackage{wasysym}
csl: resources/experimental-physiology.csl
bibliography: resources/bibliography.bib
output:
  word_document:
    reference_docx: resources/manuscript_word_template.docx
editor_options: 
  chunk_output_type: console
---
<!-- This is a comment  -->
<!-- Add comments after each reference for tracking (eg[@RN2364]<!-- comment -->
<!-- After references, add a row break without space (this will put the reference on the end on the line). -->

@@

Muscle thickness was assessed using (...) ultra sound. DXA.

@@

>>>>

---
title: "Ribosome accumulation during early phase resistance training"
author: Daniel Hammarström^1,2,£^&ast;,Sjur J. Øfsteng^2,£^, Bent R. Rønnestad^2^, Stian Ellefsen^1,3^
date: ""
header-includes:
  - \usepackage{wasysym}
csl: resources/experimental-physiology.csl
bibliography: resources/bibliography.bib
output:
  word_document:
    reference_docx: resources/manuscript_word_template.docx
editor_options: 
  chunk_output_type: console
---
<!-- This is a comment  -->
<!-- Add comments after each reference for tracking (eg[@RN2364]<!-- comment -->
<!-- After references, add a row break without space (this will put the reference on the end on the line). -->

@@

For determination of body composition participants were scanned using DXA Lunar Prodigy densitometer (GE Healthcare, Madison, WI, USA) with the standard scanning mode (13-25 cm). Participants were lying supine within the scanning bed reference lines, with a strap secured around the ankles to ensure standardised body position in each of the scans. The scans were conducted with the participants in a fasted state, with empty bladder, wearing under-wear only, between 07.00-10.00 AM. Prior to each scanning a phantom scanning was run to prevent baseline drifting from affecting analyses. The same technician was used at each time point. Analyses was performed using GE enCORE version 17.0 software (GE Healthcare). Region of interest was customized for covering upper thigh, marked with a sqaure from pubic symphysis to lateral part of tuberculum major, and distal to art. genu.

Muscle thickness (MT) was measured using a B-mode ultra sound unit (SmartUS EXT-1M, Telemed, Vilnius, Lithuania). The participant lay supine in a relaxed position for 20 min before scan, with their feet strapped to a standardized box (15x15cm). A mark was set on the line 60% of the distance between Spinia Iliac Anterior Superior and the lateral femur condyle. MT of *m.vastus lateralis* was measured applying a water-soluble transmission gel (Aquasonic 100 Ultrasound Transmission Gel; Parker Laboratories Inc., Fairfield, NJ, USA), and a 39 mm 12 MHz ultrasound probe was placed perpendicular to the site of interest without depressing the skin. When the quality of the image was satisfactory, evident as distinct upper and lower muscle fascia, three images were captured, where the probe was relocated to the same position between each image. Position of the probe was marked on the skin and subsequently marked on a transparent paper to ensure similar probe placement for both the right and left *m.vastus lateralis* at the subsequent assessments. Analyses were done in Jamovi (REF). Pictures were cropped and coded for blinding of the assessor. The average MT of the three images at each assesment was used for further analyses.

<!--Schindelin J, Arganda-Carreras I, Frise E, et al. Fiji: an open-source platform for biological-image analysis. Nat
1222 Methods. 2012;28(9(7)):676-682-->

@@

UBF levels determine rRNA gene activity throgh regulation of chromatin[@RN2556] <!--  Sanij 2008 -->

Per total RNA 
Per muscle tissue
